Proof of 2$\epsilon-$Differential Privacy

### 2018-11-01 Arxiv/main.tex
fix typos

A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } input $\dataobs, \dataobs' \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
\begin{equation*}
\mathbb{P}[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \mathbb{P}[H(\mathcal{M}(\dataobs')) \in B].
\end{equation*}

@@

A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
\begin{equation*}
\mathbb{P}[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \mathbb{P}[H(\mathcal{M}(\dataobs')) \in B] + \delta,
\end{equation*}
vwhere $\dataobs = (x_i)_{i = 1}^n$ and $\dataobs = (x'_i)_{i = 1}^n$ is adjacent if there is only one $j$ that $x_j \neq x'_j$ and $x_i = x'_i$ for $i = 1, 2, \cdots, n; i \neq j$. 
\end{definition}

@@

\subsubsection{Baseline Mechanism - Laplace Mechanism}
 Adding noise to the posterior distribution parameters directly, through Laplace mechanism ($\lap{\cdot}{\cdot}$) with post-processing:

@@

This mechanism is based on the basic exponential mechanism
\cite{talwar}, with $\candidateset$ as the range and
$\hellinger(\cdot,\cdot)$ as the scoring function. The difference is
that in this mechanism we don't calibrate the noise w.r.t. to the
global sensitivity of the scoring function but w.r.t. to the smooth
sensitivity $S(\dataobs)$ -- defined by \cite{nissim2007smooth}-- of
$\hellinger(\bysinfer(\dataobs), \cdot)$.

$\gamma = \gamma(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$ to
be determined later, and where $LS(\dataobs')$ denotes the local
sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$,
of the scoring function used in our mechanism.

@@

By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \delta) -$differentially private, where $\delta = \frac{e^{\frac{\epsilon}{2}} \delta'}{2}$.

>>>>

A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } input $\dataobs, \dataobs' \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
\begin{equation*}
\Pr[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \Pr[H(\mathcal{M}(\dataobs')) \in B].
\end{equation*}

@@

A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
\begin{equation*}
\Pr[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \Pr[H(\mathcal{M}(\dataobs')) \in B] + \delta.
\end{equation*} 
\end{definition}

@@

\subsubsection{Laplace Mechanism}
 Adding noise to the posterior distribution parameters directly, through Laplace mechanism ($\lap{\cdot}{\cdot}$) with post-processing:

@@

This mechanism is based on the standard exponential mechanism
\cite{talwar}, with $\candidateset$ as the range and
$\hellinger(\cdot,\cdot)$ as the scoring function. The difference is
that in this mechanism we don't calibrate the noise w.r.t. to the
global sensitivity of the scoring function but w.r.t. to the smooth
sensitivity $S(\dataobs)$ -- defined by \cite{nissim2007smooth}-- of
$\hellinger(\bysinfer(\dataobs), \cdot)$, where $LS(\dataobs')$ denotes the local
sensitivity at $\dataobs'$, of the scoring function used in our mechanism and  $\gamma$ is the smooth upper bound for smooth sensitivity.

@@

% By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \delta) -$differentially private, where $\delta = \frac{e^{\frac{\epsilon}{2}} \delta'}{2}$.

### 2018-11-01 notes/2epsilon/main.tex
fix typos

A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
\begin{equation*}
\mathbb{P}[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \mathbb{P}[H(\mathcal{M}(\dataobs')) \in B] + \delta,
\end{equation*}
vwhere $\dataobs = (x_i)_{i = 1}^n$ and $\dataobs = (x'_i)_{i = 1}^n$ is adjacent if there is only one $j$ that $x_j \neq x'_j$ and $x_i = x'_i$ for $i = 1, 2, \cdots, n; i \neq j$. 
\end{definition}

@@

\begin{thm}
\label{thm_gamma_smooth}
$S(\dataobs)$ is $\gamma -$smooth sensitivity if it is calculated by:
\begin{equation}
  \label{eq_smooth}
   S(\dataobs)=\max_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')} \bigg \},
\end{equation}
where $d$ is the Hamming distance between two data sets.
\end{thm}

@@

By Definition \ref{eq_smooth}:
\begin{equation*}
\begin{split}
S(\dataobs) 
& \geq \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')}\\
\frac{1}{S(\dataobs)} 
& \leq \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')\\
\end{split}
\end{equation*}

@@

  By definition \ref{def_smoo}:

  \begin{equation*}
  \begin{split}
  \hexpmechPr{\dataobs}{z = r} 
  & = \frac {exp\big(\frac{-\epsilon\cdot\ux{r}}{2\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
  & = \frac {exp\big(
  \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{2\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}} \\
  & = \frac {exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \cdot exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{2\cdot S(\dataobs)} \big)\\
  \end{split}
  \end{equation*}

@@

  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$:

  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{2} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon}{2}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
  \big)\\
  \end{split}
  \end{equation*}

  Because the property of $\gamma -$smooth sensitivity: $\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)} \leq \gamma$:

  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{2} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon}{2} \cdot \gamma
  \big)\\
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}\\
  \end{split}
  \end{equation*}
  Doing the same transformation in the denominator:

  \begin{equation*}
  \begin{split}
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\ux{r'} + \uxadj{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)}
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
  \big)
  exp 
  \big(
  \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)}
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)} \geq \frac{-\epsilon}{2}$:

  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r'})}{2\cdot S(\dataobs')}
  \big)
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'})}{2\cdot S(\dataobs')}
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  exp
  \big(
  \frac{- \epsilon\cdot(\ux{r'})}{2}
  (\frac{1}{S(\dataobs)}
-
  \frac{1}{S(\dataobs')})
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$ $\implies$ $\frac{- \epsilon\cdot(\ux{r'})}{2} \geq  \frac{-\epsilon}{2}$:

    \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  exp
  \big(
  \frac{- \epsilon}{2}
  (\frac{1}{S(\dataobs)}
-
  \frac{1}{S(\dataobs')})
  \big)
  }\\
  \end{split}
  \end{equation*}

>>>>

A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
\begin{equation*}
\Pr[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \Pr[H(\mathcal{M}(\dataobs')) \in B] + \delta,
\end{equation*}
vwhere $\dataobs = (x_i)_{i = 1}^n$ and $\dataobs = (x'_i)_{i = 1}^n$ is adjacent if there is only one $j$ that $x_j \neq x'_j$ and $x_i = x'_i$ for $i = 1, 2, \cdots, n; i \neq j$. 
\end{definition}

@@

\begin{thm}
\label{thm_gamma_smooth}
Given data set $\dataobs$ of size $n$, $S(\dataobs)$ is $\gamma -$smooth sensitivity if it is calculated by:
\begin{equation}
  \label{eq_smooth}
   S(\dataobs)=\max_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')} \bigg \},
\end{equation}
where $d$ is the Hamming distance between two data sets.
\end{thm}

@@

By Equation (\ref{eq_smooth}):
\begin{equation*}
\begin{split}
S(\dataobs) 
& \geq \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')}\\
\frac{1}{S(\dataobs)} 
& \leq \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')\\
\end{split}
\end{equation*}

@@

  By definition \ref{def_smoo}:
  \begin{equation*}
  \begin{split}
  \hexpmechPr{\dataobs}{z = r} 
  & = \frac {exp\big(\frac{-\epsilon\cdot\ux{r}}{2\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
  & = \frac {exp\big(
  \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{2\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}} \\
  & = \frac {exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \cdot exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{2\cdot S(\dataobs)} \big)\\
  \end{split}
  \end{equation*}

@@

  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$:
  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{2} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon}{2}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
  \big)\\
  \end{split}
  \end{equation*}

  Because the property of $\gamma -$smooth sensitivity: $\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)} \leq \gamma$:  
  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{2} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon}{2} \cdot \gamma
  \big)\\
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}\\
  \end{split}
  \end{equation*}

  Doing the same transformation in the denominator:
  \begin{equation*}
  \begin{split}
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\ux{r'} + \uxadj{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)}
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
  \big)
  exp 
  \big(
  \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)}
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)} \geq \frac{-\epsilon}{2}$:
  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r'})}{2\cdot S(\dataobs')}
  \big)
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'})}{2\cdot S(\dataobs')}
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  exp
  \big(
  \frac{- \epsilon\cdot(\ux{r'})}{2}
  (\frac{1}{S(\dataobs)}
-
  \frac{1}{S(\dataobs')})
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$ $\implies$ $\frac{- \epsilon\cdot(\ux{r'})}{2} \geq  \frac{-\epsilon}{2}$:
  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  exp
  \big(
  \frac{- \epsilon}{2}
  (\frac{1}{S(\dataobs)}
-
  \frac{1}{S(\dataobs')})
  \big)
  }\\
  \end{split}
  \end{equation*}
